### 2022-08-25 article.tex
Add sensitive data

When research truly needs to be reproducible, putting the code 
of an experiment into a container is a good solution, as it 
can stand the test of time well. Rewarding this, however, is not
done yet by journals.

@@

Code is paradata, as it is describes how the results are generated.
The part of a scholarly article that describes the experiment is metadata, 
as it describes what the code is thought to do.
The code that does the work in a computational experiment should
always be published together with a scholarly article,
as, if the paper and code differ, it is the code that generated the results.

For research to be reproducible, one ideally has access to
both the data used and the code.
In some fields, such as genetic epidemiology, the data is
sensitive, hence cannot be released,
yet there are methods being devised to run code on sensitive
data with assured privacy \cite{zhang2016review,azencott2018machine}.

>>>>

When research truly needs to be reproducible, putting the code 
of an experiment into a container is a good solution, as it 
can stand the test of time better.
Creating such a container, however, requires more skill
that -as of today- is not rewarded,
partly as containers follow FAIR data principles only poorly.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Sensitive data}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

For a computational experiment to be reproducible,
an independent person should be able to
reproduce the same results.
The reproduce the same results, one needs the same
input data and the same code (and the same 
dependencies and environment).
When the input data is sensitive, however, and thus cannot be shared with
an independent researcher, he/she thus cannot reproduce the
experiment.

The solution for this problem is simple:
supply a simulated dataset with the code.
In the case of genetic epidemiology this would mean
simulated genotypes and associated phenotypes,
as can be done with the \verb|plinkr| R package \cite{plinkr}.
This solution, however, is known to all developer that follow
good practices when writing code, as public (i.e. simulated) 
datasets are needed for automatic testing of code.
One extra benefit of simulated data is that these can be used
as a benchmark, as slightly different analyses should give 
similar conclusions.

@@

Code is paradata, as it directly describes how the results are generated.
The part of a scholarly article 
that describes the experiment in a natural language is metadata, 
as it describes indirectly what the code does (or should be doing).
The code that does the work in a computational experiment should
always be published together with a scholarly article,
as, if the paper and code differ, it is the code that generated the results.

For research to be reproducible, one ideally has access to
both the data used and the code.
In some fields, such as genetic epidemiology, the data is
sensitive, hence cannot be released,
yet there are methods being devised to run code on sensitive
data with assured privacy \cite{zhang2016review,azencott2018machine}.
Additionally, to ensure that
